Simulation of angular resolution of a new electromagnetic sampling calorimeter

### 2023-03-03 paper.tex
updates

\begin{abstract}
We report on the simulation results for the angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV. The simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate. The scintillator plates are alternately segmented into horizontal and vertical strips. In this study, we obtain energy deposits in individual strips using Geant4 simulations and reconstruct the incident photon angles using XGBoost with gradient-boosted decision trees. The performance of the angle reconstruction depends on the detector configuration and the accuracy of machine learning. The angular resolution is well described by the expression $0.24^{\circ} \oplus 1.25^{\circ}/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for strips of 15 mm and 32 layers. This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.

@@

In general, the sampling calorimeter enables cost-effective fabrication of large-scale detectors and design of flexible geometric configuration. This detector has been developed in various ways by selecting a material of absorber among many candidates such as brass~\cite{CMS:mat}, lead~\cite{CDF:mat}, tungsten~\cite{DELPHI:mat}, uranium~\cite{UGAS:mat}, and also of active medium such as scintillators~\cite{CMS:mat,CDF:mat}, gas~\cite{UGAS:mat}, solid-state detector~\cite{DELPHI:mat}, and liquid gas~\cite{LiqAR:mat}. Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}.

The sampling calorietmer has been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics. The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils. Tracking with the silicon detectors on the electron-positron pairs produced at the foils provides an angular resolution of 0.6 degrees for 1-GeV photons and better than 0.16 degrees for photons with energies higher than 10~GeV~\cite{FERMI:LAT}. The LAT has two additional components: a plastic scintillator for the charged-particle detection and a homogeneous CsI crystals for the energy measurement. This triple detector configuration is also used in different missions. An energy spectrum measurement of cosmic-ray electrons (CALET)~\cite{CALET} utilizes scintillating fibers and PWO crystals instead of the silicon strips and the CsI crystals, respectively. A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for the energy measurement. Theses detectors provide the angular resolution of 1-2 degrees for 1-GeV photons.

@@

The $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay is identified as a final state existing only a single $\pi^{0}$ reconstructed from detected two photons. A hermetic detector system enclosing the decay region should be prepared to confirm only two photons in the final state. There had been an experimental proposal to detect the $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with the reconstruction of a single $\pi^{0}$ using directional information of two photons~\cite{KOPIO}. A Preradiator (PR) is placed in front of the calorimeter to measure the photon's incident angle. The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and thin-gap drift chambers with cathode strips. For good energy resolution and high detection efficiency against a few hundred MeV photons, the plastic scintillator is used for electron-positron conversion. This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250-MeV~photons~\cite{KOPIOcdr}.

On the other hand, the KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with a well-collimated small-size neutral beam, which provides a condition that the $\pi^{0}$ decays at the beam axis. With this assumption, the decay vertex is calculated using the positions and energies of the two photons measured in the calorimeter. The transverse momentum of $\pi^{0}$ is calculated from the vertex. The two variables, the decay vertex and the transverse momentum are used to define a signal region of the decay. The KOTO experiment started data taking since 2013 and has achieved its experimental sensitivity as 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}. The data taking will continue for a few more years, and the sensitivity will be expected to reach $\mathcal{O}$(10$^{-11}$).

A successive experiment of the KOTO is under preparation to observe more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}. In this highly sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$. In addition, the neutrons away from the beam axis produce a $\pi^{0}$ or $\eta$ by interacting with detector materials. Two photons from those events are also one of main backgrounds. We can remove them by comparing the incident angle expected from the reconstructed vertex and the actual measurement using a new sampling calorimeter in this paper.

In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and plastic scintillator layers. There is a limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation. A deduction of the incident angle of the EM shower using a lead scintillating fiber sandwiched sampling calorimeter is studied~\cite{PbScint}, and the angular resolution is expected to be larger than 8 degrees for 1-GeV electrons. We take a machine-learning approach to get better angular resolution from the analysis. Recently, machine-learning analysis has become a critical tool for better measurement of particle identification~\cite{mlp}, timing~\cite{mlt}, and energy~\cite{mle}. We use the XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.

@@

The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator. The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}. It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.48\textwidth]{Fig2_EMShower_XZ.pdf}
\includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
\caption{ Event display of simulated energy deposit patterns for an 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
\label{fig:Evt_Dis}
\end{figure}

The detector response to the incident photons is simulated using Geant4 (ver. 4.10.06) with standard EM sub-packages~\cite{GEANT4}. The direction normal to the front surface defines the $z$-axis. The photon direction is defined by the polar angle ($\theta$) with respect to the $z$-axis. Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for an 1-GeV photon at normal incidence in the $xz$- and $yz$-planes. Each segmented region shown in Figure~\ref{fig:Evt_Dis} represents a channel.

Training data for machine learning are prepared using the Geant4 simulation such that the input dataset is representative of the detector response of the sampling calorimeter. In order to minimize the bias in the training process related to the dataset, the incident angles are uniformly generated at the detector surface in the range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes the azimuthal angle. The number of training samples is $10^{5}$ considering the limited computing resources. The angle reconstruction is studied using photons generated at given incident $\theta$ angle, energy, and position. It turns out unchanged with the energy deposit threshold above the noise level of 0.5 MeV. Therefore, we do not consider random noises in this study.

@@

The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset, the energy deposit in each scintillator strip, onto a target variable, the incident angle of a photon. The feature size identical to the number of strips varies with the strip width to have the same coverage. In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector. XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function. The hyperparameters of XGB drive how models are trained. In this paper, main five parameters are studied. \textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max. depth} defines the complexity of the decision-tree structure. \textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} weights a decision tree to be added onto the current model, and \textit{gamma} regulates the evaluation of each decision tree.

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.58\textwidth]{Fig5_width_including7.5_12.5mm.pdf}
\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
\label{fig:angle_reco_width}
\end{figure}
\subsubsection{Strip width}
To inspect the dependency of the angular resolution on the strip width, we deduce the angular resolution by varying the strip width from 5 to 35mm, as shown in Figure~\ref{fig:angle_reco_width}. The narrower the strip width, the larger the feature size. Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than with 5-mm-wide strips. However, the wider strips hardly provide detailed information on the EM shower. The 15-mm-wide strips yield a good angular resolution of 1.24~$\pm$~0.01$^{\circ}$ and are selected for further study considering the actual construction of a prototype detector, although 10-mm-wide strips provide the best resolution.

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{Fig6_layer_comp.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{ 
\includegraphics[width=0.48\textwidth]{Fig6_nlayer.pdf}
}
\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$  with the front 32 layers of 15-mm-wide strips. The red histogram represents the angular distribution after requiring $E_{\rm{tot}}>$~10~MeV for the front layers. (b) Angular resolution as a function of the radiation length ($X_{0}$) with the front layers. The red line corresponds to the results using entire layers of 105.}
\label{fig:angle_reco_layer}
\end{figure}

\subsubsection{Number of layers}
We study the dependency of the angle reconstruction on the number of front layers. Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2$X_{0}$. A fraction of the photons fails to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%. The failed events are represented as a delta function near 0. Such events are removed by requiring the total energy deposit at the front layers to be higher than 10~MeV, which is 1\% of the incident energy. The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$. The evolution of angular resolution degrades with the reduction of the number of layers used.

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.6\textwidth]{Fig8_nsample_400k_500k.pdf}
\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers. The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$. }
\label{fig:multi-parameter}
\end{figure}

@@

The spectra are fitted with the empirical function of $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ describe the decreasing trend. The numbers of training samples reaching the angular resolution of 1.1$I$ with 25-, 15-, and 5-mm-wide strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.

@@

The width of strips to record the energy deposit of shower particles is an essential parameter of the angular resolution, which should be compromised between the required angular resolution and construction costs related to the number of read-out channels. In addition, the angular resolution is also determined by the training accuracy of the XGBoost, which requires a different number of training data according to the detector configuration. When we test a detector configuration with many channels (i.e., narrow strip), we should also prepare a large number of data for the training.

@@

@@

\bibitem{KOTObeam}
T. Shimogawa, Nucl. Instrum. Meth. A {\bf 623} (2010) 585-587

@@

>>>>

\begin{abstract}
We report on the simulation results for the angular resolution of an electromagnetic (EM) sampling calorimeter with photons in the range of 100~MeV to 2~GeV. The simulation model of the EM calorimeter consists of alternating layers of a 1-mm-thick lead plate and a 5-mm-thick plastic scintillator plate. The scintillator plates are alternately segmented into horizontal and vertical strips. In this study, we obtain energy deposits in individual strips using Geant4 simulations and reconstruct the incident photon angles using XGBoost with gradient-boosted decision trees. The performance of the angle reconstruction depends on the detector configuration and the accuracy of machine learning. The angular resolution is well described by the expression $0.24^{\circ} \oplus 1.25^{\circ}/\sqrt{E_{\gamma}}$, where $E_{\gamma}$ is the incident photon energy in GeV, for 32 layers of 15~mm width strips. This energy dependence is consistent for different incident angles in the range of 10$^{\circ}$ to 40$^{\circ}$.

@@

In general, the sampling calorimeter enables cost-effective fabrication of large-scale detectors and design of flexible geometric configuration. This detector has been developed in various ways by selecting a material of absorber among many candidates such as brass~\cite{CMS:mat}, lead~\cite{CDF:mat}, tungsten~\cite{DELPHI:mat}, uranium~\cite{UGAS:mat}, and also of active medium such as scintillators~\cite{CMS:mat,CDF:mat}, gas~\cite{UGAS:mat}, solid-state detector~\cite{DELPHI:mat}, and liquid gas~\cite{LiqAR:mat}. Also, there are many topologies to pile up the materials and read out their signals, such as sandwich~\cite{KOTO:MB}, shashlik~\cite{shashlik:con}, spaghetti~\cite{KLOE:con}, and accordian~\cite{LiqAR:mat}. Sampling calorimeters have been used to measure the direction of arriving photons in a space-based detector to identify astrophysical sources for gamma-ray astrophysics. The PAMELA experiment employs a strip multilayer electromagnetic calorimeter of 22 ($x$,$y$) layers of silicon strip detectors interleaved with 22 tungsten plates, which identifies the particle types and measures the deposited energy, and helps to determine the detection of the particles~\cite{PAMELA}. The Fermi Large Area Telescope (LAT) has a tracker consisting of 18 $x$-$y$ pairs of silicon strip detectors with 16 interleaved tungsten foils. Tracking with the silicon detectors on the electron-positron pairs produced at the foils provides an angular resolution of 0.6 degrees for 1-GeV photons and better than 0.16 degrees for photons with energies higher than 10~GeV~\cite{FERMI:LAT}. The LAT has two additional components: a plastic scintillator for the charged-particle detection and a homogeneous CsI crystals for the energy measurement. This triple detector configuration is also used in different missions. An energy spectrum measurement of cosmic-ray electrons (CALET)~\cite{CALET} utilizes scintillating fibers and PWO crystals instead of the silicon strips and the CsI crystals, respectively. A dark matter particle explorer mission (DMPE)~\cite{DMPE} selects BGO crystals for the energy measurement. Theses detectors provide the angular resolution of 1-2 degrees for 1-GeV photons.

@@

The $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay is identified as a final state existing only a single $\pi^{0}$ reconstructed from detected two photons. A hermetic detector system enclosing the decay region should be prepared to confirm only two photons in the final state. There had been an experimental proposal to detect the $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with the reconstruction of a single $\pi^{0}$ using directional information of two photons~\cite{KOPIO}. A Preradiator (PR) is placed in front of the calorimeter to measure the photon's incident angle. The PR consists of a close-packed multi-layer sandwich of 8-mm-thick plastic scintillators alternating with the single-plane and thin-gap drift chambers with cathode strips. This idea had been confirmed by a beam test using tagged photon beams and achieved its angular resolution of 25~mrad for 250-MeV~photons~\cite{KOPIOcdr}.

The KOTO experiment at J-PARC~\cite{KOTOexp} takes another approach to identify $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decay with the help of a well-collimated and small-size neutral beam, constraining the $\pi^{0}$ decays along the beam axis. With this assumption, the decay vertex is calculated using the positions and energies of the two photons measured in the calorimeter. The transverse momentum of $\pi^{0}$ is calculated from the vertex. The two variables, the decay vertex and the transverse momentum are used to define a signal region of the decay. The KOTO experiment started data taking in 2013 and has achieved an experimental sensitivity of 7.2~$\times$~10$^{-10}$~\cite{KOTOexp}. The data taking will continue for a few more years, and the sensitivity is expected to reach $\mathcal{O}$(10$^{-11}$), close to the detection limit for a branching fraction near 3~$\times$~10$^{-11}$

A successor experiment to the KOTO is aiming at observing more than 35 $K_{L} \rightarrow \pi^{0}\nu\bar{\nu}$ decays with a higher-intensity beam and a larger-scale detector system~\cite{KOTO2}. In this highly sensitive measurement, the halo kaon, which is scattered by beam line materials and decays at off-beam axis, will become a considerable background source when the kaon decays via $K_{L} \rightarrow 2\gamma$. In addition, the off-axis neutrons could produce a $\pi^{0}$ or $\eta$ by interacting with detector materials. Two photons from those events are also one of main backgrounds. We can remove them by comparing the incident angle expected from the reconstructed vertex and the actual measurement using a new sampling calorimeter.

In this respect, we report on results of Monte Carlo studies on directional measurement analyzing energy-weighted shower shapes generated in a toy sampling calorimeter, which consists of segmented alternating lead and plastic scintillator layers. There is an intrinsic limitation in the angular resolution from the analysis of shower shape produced in a sampling calorimeter due to the stochastic feature of its generation. In a previous study~\cite{PbScint}, a deduction of the incident angle of the EM shower using a similar lead-scintillator sandwiched sampling calorimeter, with a cell size of 9~$\times$~9~mm$^{2}$, is expected to be larger than 8 degrees for 1-GeV electrons. In this study, we apply a machine-learning approach to improve angular resolution from the analysis. Recently, machine-learning analysis has become a critical tool for better measurement of particle identification~\cite{mlp}, timing~\cite{mlt}, and energy~\cite{mle}. We use the XGBoost (XGB), which is an optimized distributed gradient-boosting library~\cite{xgboost:2016}.

@@

The toy sampling calorimeter is designed as a block consisting of alternating layers of an 1-mm-thick lead absorber and a 5-mm-thick polyvinyltoluene-based plastic scintillator. The plastic scintillator is segmented into 15-mm-wide strips, which are alternately oriented in the vertical and horizontal directions, as shown in Figure~\ref{fig:det_conf}. It has a cross-section size of 525~$\times$~525~mm$^{2}$ and accommodates 105 alternating layers of 630~mm length and 20 radiation lengths (20$X_{0}$) to contain the EM shower of photons for energies in the range of 0.1 to 2~GeV.

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.48\textwidth]{Fig2_EMShower_XZ.pdf}
\includegraphics[width=0.48\textwidth]{Fig2_EMShower_YZ.pdf}
\caption{ Event display of simulated energy deposit patterns for a 1-GeV photon entering the calorimeter ($\theta=$~0) in (a) $xz$- and (b) $yz$-planes.}
\label{fig:Evt_Dis}
\end{figure}

The detector response to the incident photons is simulated using Geant4 (ver. 4.10.06) with standard EM sub-packages~\cite{GEANT4}. The direction normal to the front surface defines the $z$-axis. The photon direction is defined by the polar angle ($\theta$) with respect to the $z$-axis. Figure~\ref{fig:Evt_Dis} illustrates the simulated energy deposit patterns in each strip for a 1-GeV photon at normal incidence in the $xz$- and $yz$-planes. Each segmented region shown in Figure~\ref{fig:Evt_Dis} represents a channel.

Training data for machine learning are prepared using the Geant4 simulation such that the input dataset is representative of the detector response of the sampling calorimeter. In order to minimize the bias in the training process related to the dataset, the incident angles are uniformly generated at the detector surface in the range of 0~$<\theta<$~50$^{\circ}$ and 0~$<\varphi<$~360$^{\circ}$, where $\varphi$ denotes the azimuthal angle. The number of training samples is $10^{5}$ considering the limited computing resources. The angle reconstruction is studied using photons generated at given incident $\theta$ angle and fixed incident energy and incident position. It turns out to be unchanged with the energy deposit threshold above the noise level of 0.5 MeV. Therefore, we do not consider random noises in this study.

The angular reconstruction can be largely affected by the deviation of the incident position, coming from the spatial resolution of the incident position reconstruction, which can be overcome with the repetitive training for different incident positions. In this study, such effects are not considered when evaluating the angular resolution. The position resolution is expected to be level of 3~mm and to degrade the angular resolution as much as 40\%.

@@

The incident angle of the photons is reconstructed using XGB~\cite{xgboost:2016}, which maps a feature dataset onto a target variable. Here, the feature dataset and the target varialbe correspond to the energy deposit in each scintillator strip and the incident angle of a photon, respectively. The feature dataset size is the number of strips, hence it varies inversely to the strip width to have the same coverage. In the case of the 15-mm-wide strips, 35~$\times$~105 channels compose the detector. XGB constructs gradient-boosted decision trees using the training dataset, efficiently descending the loss function. The hyperparameters of XGB drive how models are trained. In this paper, five main parameters are studied. \textit{N\_estimators} defines the maximum number of allowed decision trees to be developed, and \textit{Max. depth} defines the complexity of the decision-tree structure. \textit{Subsample} controls the fraction of total event samples for each boosting procedure, \textit{learning rate} determines the step length of gradient boosting, and \textit{gamma} regulates the evaluation of each decision tree.

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.58\textwidth]{Fig5_width_including7.5_12.5mm.pdf}
\caption{ Angular resolutions are deduced in terms of the strip width for 1-GeV photons at $\theta=$~10$^{\circ}$ }
\label{fig:angle_reco_width}
\end{figure}
\subsubsection{Strip width}
To inspect the dependency of the angular resolution on the strip width, we deduce the angular resolution by varying the strip width from 5 to 35mm, as shown in Figure~\ref{fig:angle_reco_width}, where each point is obtained through the fit procedure. The narrower the strip width, the larger the feature dataset size. Consequently, the angle-reconstruction performance is better with 10-mm-wide strips than with 5-mm-wide strips. However, the wider strips hardly provide detailed information on the EM shower. The 15-mm-wide strips yield an angular resolution of 1.24(1)~$\pm$~0.01$^{\circ}$ for photons impacting at the center of the strips and are selected for further study considering the actual construction of a prototype detector, although 10-mm-wide strips provide the best resolution.

\begin{figure}[!hbt]
\centering
\stackinset{c}{0.cm}{b}{-0.4cm}{(a)}{
\includegraphics[width=0.48\textwidth]{Fig6_layer_comp.pdf}
}\stackinset{c}{0.cm}{b}{-0.4cm}{(b)}{ 
\includegraphics[width=0.48\textwidth]{Fig6_nlayer.pdf}
}
\caption{ (a) Reconstructed polar angles ($\theta$) for 1-GeV photons at $\theta=$~10$^{\circ}$  with the front 32 layers of 15-mm-wide strips. The red histogram represents the angular distribution after requiring $E_{\rm{tot}}>$~10~MeV for the front layers. (b) Angular resolution as a function of the radiation length ($X_{0}$) with the front layers. The red solid line represented as Full layer in the legend corresponds to the results using entire layers.}
\label{fig:angle_reco_layer}
\end{figure}

\subsubsection{Number of layers}
We study the dependency of the angle reconstruction on the number of front layers. Figure~\ref{fig:angle_reco_layer} (a) shows the reconstructed angular distribution for 1-GeV photons by using only the front 32 layers, which correspond to 6.2~$X_{0}$. A fraction of the photons fails to be reconstructed because of insufficient information gathering caused by deeply penetrating photons without shower generation, where the fraction is estimated to be 1.9\%. The failed events are represented as a delta function near 0. Such events are removed by requiring the total energy deposit at the front layers to be higher than 10~MeV, which is 1\% of the incident energy. The angular resolution with the front 32 layers is estimated to be 1.30~$\pm$~0.01$^{\circ}$. The evolution of angular resolution degrades with the reduction of the number of layers used, as shown in figure~\ref{fig:angle_reco_layer} (b).

@@

\begin{figure}[!hbt]
\centering
\includegraphics[width=0.6\textwidth]{Fig8_nsample_400k_500k.pdf}
\caption{ The angular resolution for 1-GeV photons at $\theta=$~10$^{\circ}$ as a function of the number of training samples with different strip widths obtained using the first 32 layers or the full layers. The spectra are fitted with $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$.}
\label{fig:multi-parameter}
\end{figure}

@@

The spectra in figure~\ref{fig:multi-parameter} are fitted with the empirical function, $\sqrt{I^{2} + (D/N_{\mathrm{sample}})^{k}}$, where $I$ denotes the intrinsic resolution and $D$ and $k$ describe the decreasing trend. The numbers of training samples reaching the angular resolution of 1.1$I$ with 25-, 15-, and 5-mm-wide strips are estimated to be 58k, 280k, and 7.6M, respectively, indicating that the number of training samples are insufficient especially for 5-mm-wide strips.

@@

The width of strips to record the energy deposit of shower particles is an essential parameter of the angular resolution, which should be compromised between the required angular resolution and construction costs related to the number of read-out channels. In addition, the angular resolution is also determined by the training accuracy of the XGBoost, which requires a different number of training data according to the detector configuration. We also emphasize on the interplay between the number of channels and training samples.

@@

\bibitem{PAMELA}
S. V. Borisov {\it et al.}, Instrum Exp Tech 56, 1–8 (2013)

@@

@@

%\bibitem{KOTObeam}
%T. Shimogawa, Nucl. Instrum. Meth. A {\bf 623} (2010) 585-587
